### 2023-05-08 docs/minutes/slides/document.tex
try ultranest sampler

	\begin{itemize}
		\item Problem = overly narrow,biased posteriors 
	\end{itemize}

@@

\begin{frame}{}
	A match made in heaven: reduced precision + stochastic rounding \newline

	   \centering
		\begin{tikzpicture}
    \draw [-,>=stealth, color = black, thick] (-5, 0.0) -- (+5, 0.0); 
     \draw [densely dashed,>=stealth, color = black, thick] (0.0, -0.50) -- (0.0, +0.5); 
      \draw [-,>=stealth, color = black, thick] (-3, -0.50) -- (-3, +0.5); 
	\draw [-,>=stealth, color = black, thick] (+3, -0.50) -- (+3, +0.5); 
	\node[text=blue] at (3.2, -0.5) {$x_2$};
	\node[text=blue] at (-2.8, -0.5) {$x_1$};
	\node[text=blue] at (1.5, 1.2) {$x$};
	\draw [-stealth,color = blue, thick] (1.5, 1.01) -- (1.5, 0.0);

	\draw [-,>=stealth, color = red, thick] (-5, 1.0) -- (+5, 1.0);

	\end{tikzpicture}

\raggedright

\begin{itemize}
	\item Usual way: Round-to-nearest
	\item Alternatively: Round \alert{stochastically} 
\end{itemize}

Why bother? $\rightarrow \mathbb{E} \left(\mathcal{R}(x)\right) = x$

@@

\begin{frame}{}
\centering
\vspace{5mm}
%\includegraphics[width=0.75\textwidth,height=0.75\textwidth]{images/precip_ensemble_timeseries_decadal}

\raggedleft
\vspace{-1mm}
\tiny \url{arxiv.org/abs/2207.14598} \normalsize

@@

>>>>

	\begin{itemize}
		\item \alert{Problem = overly narrow,biased posteriors}. Even for ``easy" systems!
	\end{itemize}

\includegraphics[width=0.5\textwidth,height=0.5\textwidth]{images/example_system}

$h = 10^{-2}, \sigma_m = 10^{-13}, \sigma_p = 0.0$

@@

	\begin{itemize}
		\item Why? Very nasty likelihood curves
	\end{itemize}

	$$  p(\theta | d) \propto p(d | \theta) \pi({\theta})$$
	$$ p(\theta | d) \propto \mathcal{L}(\theta) \pi({\theta})$$

	For uniform prior, posterior shape $\sim$ likelihood shape.

@@

	Example: $\mathcal{L}(\delta)$

\includegraphics[width=0.7\textwidth,height=0.6\textwidth]{images/likelihood_delta_1}

@@

	Example: $\mathcal{L}(\delta)$, zoomed 1

	\includegraphics[width=0.7\textwidth,height=0.6\textwidth]{images/likelihood_delta_2}

	Example: $\mathcal{L}(\delta)$, zoomed 2

	\includegraphics[width=0.7\textwidth,height=0.6\textwidth]{images/likelihood_delta_3}

	Example: $\mathcal{L}(\omega)$

	\includegraphics[width=0.7\textwidth,height=0.6\textwidth]{images/likelihood_omega_1}

	Example: $\mathcal{L}(\omega)$, zoomed 1

	\includegraphics[width=0.7\textwidth,height=0.6\textwidth]{images/likelihood_omega_2}

	Example: $\mathcal{L}(\omega)$, zoomed 2

	\includegraphics[width=0.7\textwidth,height=0.6\textwidth]{images/likelihood_omega_3}

	All likelihood curves for $\bar{\theta}_{\rm GW}$:

	\includegraphics[width=0.9\textwidth,height=0.7\textwidth]{images/all_likelihood_curves}

		\begin{itemize}
		\item \alert{Problem} = overly narrow,biased posteriors
		\item Cause: noisy, likelihoods which are "locally Gaussian". Sampling gets stuck in a local optima and infers posteriors widths based on that optima. 
	\end{itemize}

\begin{frame}{}
	Potential solutions:

	\begin{enumerate}
		\item Don't be a Bayesian: Maximum likelihood / loss optimisation? 
		\item Be a Bayesian: Drop PSR terms from model?
		\item other...?
	\end{enumerate}

\begin{frame}{Option 2: Drop PSR terms from model?}
	 \begin{equation}
		f_{\rm measured} = f_{\rm emitted} \, g(\tau; \bar{\theta})
		\label{eq:measureent}
	\end{equation}
	with
	\begin{align}
		g(\tau; \bar{\theta}) 
		& = 1 - \frac{1}{2} \frac{ H_{ij}q^i q^j }{(1 + \bar{n}\cdot \bar{q}) } \left[ \cos(-\Omega \tau +\Phi_0) - \cos(-\Omega \tau +\Phi_0 + \Omega (1 + \bar{n}\cdot \bar{q})  d) \right]
	\end{align}

Generate the fake data using the full expression for $g(\tau; \bar{\theta})$, but use $g'(\tau; \bar{\theta})$ in the Kalman measurement model

		\begin{align}
		g'(\tau; \bar{\theta}) 
		& = 1 - \frac{1}{2} \frac{ H_{ij}q^i q^j }{(1 + \bar{n}\cdot \bar{q}) } \left[ \cos(-\Omega \tau +\Phi_0) \right]
	\end{align}
\end{frame}

\begin{frame}{Option 2: Drop PSR terms from model?}

		All likelihood curves for $\bar{\theta}_{\rm GW}$:
		\includegraphics[width=0.9\textwidth,height=0.7\textwidth]{images/all_likelihood_curves_psr}

\begin{frame}{Option 2: Drop PSR terms from model?}

	All likelihood curves for $\bar{\theta}_{\rm GW}$:
	\includegraphics[width=0.9\textwidth,height=0.7\textwidth]{images/all_likelihood_curves_psr}

\begin{frame}{Option 2: Drop PSR terms from model?}

	\includegraphics[width=0.9\textwidth,height=0.7\textwidth]{images/canonical_mixed_result}

	OK, but some biases...
\end{frame}
